This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-10 article.tex
prevented an unwanted en-dash

In the previous section, recall that we created the minimal PoC by
patching the command line arguments to \texttt{pack-objects}.  One of
the command line arguments that is already passed by default
is \texttt{--delta-base-offset}. Running \texttt{git help
pack-objects} reveals the following:
\begin{center}
{\footnotesize\setbox9\hbox{\verb|A packed archive can express the base object of a delta as either a|}
\begin{minipage}{\wd9}
\begin{verbatim}
A packed archive can express the base object of a delta as either a
20-byte object name or as an offset in the stream, but ancient
versions of Git don't understand the latter. By default, git
pack-objects only uses the former format for better compatibility.
This option allows the command to use the latter format for
compactness. Depending on the average delta chain length, this
option typically shrinks the resulting packfile by 3-5 per-cent.
\end{verbatim}
\end{minipage}}
\end{center}
So all we need to do is \emph{remove} the \texttt{--delta-base-offset}
argument and git will not include any offset delta objects in the
pack!

>>>>

In the previous section, recall that we created the minimal PoC by
patching the command line arguments to \texttt{pack-objects}.  One of
the command line arguments that is already passed by default
is \texttt{-{}-delta-base-offset}. Running \texttt{git help
pack-objects} reveals the following:
\begin{center}
{\footnotesize\setbox9\hbox{\verb|A packed archive can express the base object of a delta as either a|}
\begin{minipage}{\wd9}
\begin{verbatim}
A packed archive can express the base object of a delta as either a
20-byte object name or as an offset in the stream, but ancient
versions of Git don't understand the latter. By default, git
pack-objects only uses the former format for better compatibility.
This option allows the command to use the latter format for
compactness. Depending on the average delta chain length, this
option typically shrinks the resulting packfile by 3-5 per-cent.
\end{verbatim}
\end{minipage}}
\end{center}
So all we need to do is \emph{remove} the \texttt{-{}-delta-base-offset}
argument and git will not include any offset delta objects in the
pack!
